Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-01 paper.tex
Address reviewer 2 comments in abstract

\begin{abstract}
    The near-wake of a vertical-axis cross-flow turbine (CFT) was modeled
    numerically via blade-resolved $k$--$\omega$ SST and Spalart--Allmaras RANS
    models in two and three dimensions. Results for each case are compared with
    experimental measurements of the turbine shaft power, overall drag, mean
    velocity, turbulence kinetic energy, and momentum transport terms in the
    near-wake at one diameter downstream. It was shown that 2-D simulations
    overpredict turbine loading and do not resolve mean vertical momentum
    transport, which plays an important role in the near-wake's momentum
    balance. The 3-D simulations fared better at predicting performance, with
    the Spalart--Allmaras model predictions being closest to the experiments.
    The SST model more accurately predicted the turbulence kinetic energy while
    the Spalart--Allmaras model more closely matched the momentum transport
    terms in the near-wake. These results show the potential of blade-resolved
    RANS as a design tool and a way to ``extrapolate'' experimental flow field
    measurements.
\end{abstract}

>>>>

\begin{abstract}
    The near-wake of a vertical-axis cross-flow turbine (CFT) was modeled
    numerically via blade-resolved $k$--$\omega$ SST and Spalart--Allmaras RANS
    models in two and three dimensions. Results for each case were compared with
    experimental measurements of the turbine shaft power, overall streamwise
    rotor drag, mean velocity, turbulence kinetic energy, and momentum transport
    terms in the near-wake at one diameter downstream. It was shown that 2-D
    simulations overpredict turbine loading and do not resolve mean vertical
    momentum transport, which plays an important role in the near-wake's
    momentum balance. The 3-D simulations fared better at predicting
    performance, with the Spalart--Allmaras model predictions being closest to
    the experiments. The SST model more accurately predicted the turbulence
    kinetic energy while the Spalart--Allmaras model more closely matched the
    momentum transport terms in the near-wake. These results show the potential
    of blade-resolved RANS as a design tool and a way to ``extrapolate''
    experimental flow field measurements.
\end{abstract}
